---
title: "Plot Generation for Distributed Robust Inference"
output: html_document
---

### Introduction

This document generates visualizations for the coverages and widths of distributed confidence intervals under across various configurations of contamination proportions and scales. It compares the performance of 

(1) M-boot: distributed bootstrap CI for distributed M estimator
(2) Debias-M-boot: debiased distributed bootstrap CI for distributed M estimator
(3) M-normal: asymptotic normality based CI for distributed M estimator
(4) OLS-normal: asymptotic normality based CI for global OLS estimator


```{r setup, include=FALSE}
# Load required libraries
library(ggplot2)
library(tidyverse)
library(dplyr)
# Set global chunk options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```


### Load Data


```{r}
# Load data
df <- read.csv('results/output_CI_epsilon.csv')
df$proportion<-round(df$proportion,4)*100
# Coverage results
df_freq = df%>%filter(type=='freq'|type=='freq_fix'|type=='freq_plugin'|type=='freq_ols')%>%group_by(scale,proportion,type)%>%summarise(freq=mean(results))
df_freq
# Width results
df_width = df%>%filter(type=='width'|type=='width_fix'|type=='width_plugin'|type=='width_ols')%>%group_by(scale,proportion,type)%>%summarise(width=mean(results))
df_width
```





### Coverage Plots


```{r}
# Rename estimator types for readability
df <- df_freq
colnames(df)[3] <- 'Methods'
df <- df %>% mutate(Methods = str_replace(Methods, "freq_fix", "Debias-M-boot"))
df <- df %>% mutate(Methods = str_replace(Methods, "freq_ols", "OLS-Normal"))
df <- df %>% mutate(Methods = str_replace(Methods, "freq_plugin", "M-Normal"))
df <- df %>% mutate(Methods = str_replace(Methods, "freq", "M-boot"))
df_freq <- df
df_freq
```


```{r}
scale_labels <- c(
  '1' = "G = X1",
  '10' = "G = 10*X1",
  '100' = "G = 100*X1"
)
df_freq%>%
#%>%filter(type=='freq'|type=='freq_norm')%>%
ggplot(aes(x =as.factor(proportion), y = freq,group=Methods,color=Methods)) +geom_line(position = position_dodge(width = 0.2))+geom_point()+coord_cartesian(ylim = c(0, 1))+geom_hline(yintercept=0.95)+ 
  facet_wrap(~scale,scales = "free", labeller = labeller(scale = scale_labels))+theme_bw()+labs(
       y = "Coverage", x = "Contamination Proportion (%)")  +
  theme()
ggsave(file="results/CI_freq_epsilon.pdf", width=8, height=3, dpi=1000)
```


### Width Plots

```{r}
df <- df_width
colnames(df)[3] <- 'Methods'
df <- df %>% mutate(Methods = str_replace(Methods, "width_fix", "Debias-M-boot"))
df <- df %>% mutate(Methods = str_replace(Methods, "width_ols", "OLS-Normal"))
df <- df %>% mutate(Methods = str_replace(Methods, "width_plugin", "M-Normal"))
df <- df %>% mutate(Methods = str_replace(Methods, "width", "M-boot"))
df_width <- df
df_width
```

```{r}
scale_labels <- c(
  '1' = "G = X1",
  '10' = "G = 10*X1",
  '100' = "G = 100*X1"
)

df_width%>%
#%>%filter(type=='freq'|type=='freq_norm')%>%
ggplot(aes(x =as.factor(proportion), y = width,group=Methods,color=Methods)) +geom_line(position = position_dodge(width = 0.2))+geom_point()+coord_cartesian(ylim = c(0, 0.3))+
  facet_wrap(~scale,scales = "free",labeller = labeller(scale = scale_labels))+theme_bw()+labs(
       y = "Width", x = "Contamination Proportion (%)") 
ggsave(file="results/CI_width_epsilon.pdf", width=8, height=3, dpi=1000)

```


