---
title: "Plot Generation for Distributed Robust M-Estimation"
output: html_document
---

## Introduction

This document generates visualizations for the simulation results of the distributed M-estimator (Huber) under different configurations of (1) noise distribution F and contamintion distribution G; (2) contamination proportion and scale; (3) local sample size n.

```{r setup, include=FALSE}
# Load required libraries
library(ggplot2)
library(tidyverse)
library(dplyr)
# Set global chunk options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```




## Part I: Effect of noise distribution F and contamintion distribution G 

```{r}
# Load the output CSV
df <- read.csv("results/output_FG.csv")

# Display the first few rows
head(df)

# Convert G to a factor with specific levels for ordered display
df$G_factor <- factor(df$G, levels = c('X1', 'sum(X)', 'unif[-|y0|,|y0|]', 'sgn(y0)*F'))

# Set F to a factor with the desired order of levels
df$F_factor <- factor(df$F, levels = c('normal', 't', 'lognorm', 'pareto'))

# Filter data for the required estimation types
filtered_df <- df %>% 
  filter(type %in% c('ols_global', 'Huber_global', 'Huber_distr_dc'))

# Update labels for F and G to be more descriptive
F_labels <- c(
  'pareto' = "F = Pareto",
  'lognorm' = "F = Log-normal",
  't' = "F = t",
  'normal' = "F = Normal"
)
G_labels <- c(
  'X1' = "G = 10*X1",
  'sum(X)' = "G = 10*sum(X)",
  'unif[-|y0|,|y0|]' = "G = 10*unif[-|y0|,|y0|]",
  'sgn(y0)*F' = "G = 10*sgn(y0)*F"
)


# Plot with a 4x4 grid layout
ggplot(filtered_df, aes(x = type, y = err, fill=type)) +
  geom_boxplot() +
  facet_grid(F_factor ~ G_factor, labeller = labeller(F_factor = F_labels, G_factor = G_labels)) + # Custom labels for F and G
  theme_bw() +
  coord_cartesian(ylim = c(0, 1)) +
  theme(
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1, face = "bold"),  # Increase size for x-axis tick labels
    axis.text.y = element_text(size = 10),  # Increase size for y-axis tick labels
    axis.title.x = element_text(size = 14, face = "bold"),  # Increase x-axis label font size
    axis.title.y = element_text(size = 14, face = "bold"),  # Increase y-axis label font size
    strip.text = element_text(size = 11, face = "bold"),  # Larger, bold subplot titles
  ) +
  labs(x = "Estimator Type", y = "Estimation Error") +
  scale_x_discrete(labels = c('Distr-M', 'Global-M', 'Global-OLS')) + # Label each type
  guides(fill = "none")  # Remove the legend

# Save the plot
ggsave(file = "results/err_FG.pdf", width = 8, height = 8, dpi = 1000)

```




## Part II: Effect of contamination proportion and scale 


```{r}
# Load the output CSV
df <- read.csv("results/output_epsilon.csv")

# Display the first few rows
head(df)

# Filter data for the required estimation types
filtered_df <- df %>% 
  filter(type %in% c('ols_global', 'Huber_global', 'Huber_distr_dc'))

# Rename methods for readability
colnames(df)[5] <- 'Methods'
df <- df %>% 
  mutate(Methods = str_replace(Methods, "ols_global", "Global-OLS"),
         Methods = str_replace(Methods, "Huber_distr_dc", "Distr-M"),
         Methods = str_replace(Methods, "Huber_global", "Global-M"))

# Convert proportion to factor for proper ordering in plot
df$proportion <- as.factor(df$proportion)

scale_labels <- c(
  '1' = "G = X1",
  '10' = "G = 10*X1",
  '100' = "G = 100*X1"
)


# Plot with boxplots for each estimator type and median lines across contamination proportions
ggplot(df %>% filter(Methods %in% c('Global-OLS', 'Distr-M', 'Global-M')),
       aes(x = proportion, y = err, fill = Methods)) +
  geom_boxplot(position = position_dodge(width = 0.8)) +  # Boxplots with dodge to separate Methods
  stat_summary(fun = median, geom = "line", aes(group = Methods, color = Methods),
               position = position_dodge(width = 0.8)) +  # Median line for each Methods group
  stat_summary(fun = median, geom = "point", aes(group = Methods, color = Methods), 
               position = position_dodge(width = 0.8), size = 1.5) +  # Points on median line
  theme_bw() +
  facet_wrap(~scale, scales = "free", labeller = labeller(scale = scale_labels)) +  # One plot per scale
  coord_cartesian(ylim = c(0, 10)) +
  labs(y = "Estimation Error", x = "Contamination Proportion") +
  theme(
    axis.text.x = element_text(size = 12, face = "bold"),  # Increase size for x-axis tick labels
    axis.text.y = element_text(size = 12, face = "bold"),  # Increase size for y-axis tick labels
    axis.title.x = element_text(size = 15, face = "bold", margin = margin(t = 10)),  # Increase x-axis label font size
    axis.title.y = element_text(size = 15, face = "bold"),  # Increase y-axis label font size
    strip.text = element_text(size = 15, face = "bold"),  # Larger, bold subplot titles
  ) +
  scale_fill_discrete(name = "Estimator Type")  +
  scale_color_discrete(name = "Estimator Type")  # Ensure colors for lines match boxplot fill colors

#+  # Fill color for boxplots by estimator type
#  scale_color_manual(values = c('blue', 'red', 'green'), name = "Methods")  # Line color for each estimator type

# Save the plot
ggsave(file = "results/err_epsilon.pdf",
       width = 12, height = 5, dpi = 1000)

```


## Part III: Effect of local sample size n 


```{r}
# Load the output CSV
df <- read.csv("results/output_n.csv")

# Display the first few rows
head(df)

# Filter data for the required estimation types
filtered_df <- df %>% 
  filter(type %in% c('ols_global', 'Huber_global', 'Huber_distr_dc'))

# Update labels for n to be more descriptive
n_labels <- c(
  '500' = "n=500",
  '1000' = "n=1000",
  '2500' = "n=2500",
  '5000' = 'n=5000',
  '10000' = 'n=10000'
)

# Create a plot for the estimation error
df %>%
  filter(type %in% c('ols_global', 'Huber_global', 'Huber_distr_dc') & n != 7500) %>%
  mutate(type = factor(type, levels = c('Huber_distr_dc', 'Huber_global', 'ols_global'), 
                       labels = c('Distr-M', 'Global-M', 'Global-OLS'))) %>%
  ggplot(aes(x = type, y = err, fill = type)) +
  geom_boxplot() +
  facet_wrap(~n, scales = "free_y", ncol = 5, labeller = labeller(n = n_labels)) +  # Set free_y if errors vary widely with n
  theme_bw() +
  coord_cartesian(ylim = c(0, 0.08)) +  # Adjust y-limits as needed
  scale_fill_discrete(name = "Methods") +
  theme(
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1, face = "bold"),  # Increase size for x-axis tick labels, angled for clarity
    axis.text.y = element_text(size = 10),  # Increase size for y-axis tick labels
    axis.title.x = element_text(size = 13, face = "bold"),  # Increase x-axis label font size
    axis.title.y = element_text(size = 13, face = "bold"),  # Increase y-axis label font size
    strip.text = element_text(size = 11, face = "bold"),  # Larger, bold subplot titles
    legend.position = "bottom",  # Place legend at the bottom for a cleaner look
    legend.title = element_text(size = 12),  # Legend title size
    legend.text = element_text(size = 10)    # Legend text size
  ) +
  labs(
    y = "Estimation Error", x = "Estimator Type"
  )+
  guides(fill = "none")  # Remove the legend


# Save the plot
ggsave(file = "results/err_n.pdf", width = 9.5, height = 4, dpi = 1000)

```
